%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Backend Team Lead} % Job title
    {SabaIdea} % Organisation
    {Tehran, Iran} % Location
    {April 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Led a backend team of 4 engineers for the Aparat Short project - a short video platform with over 500K active users.
        \item Was fully responsible for the project’s architecture, delivery, and prioritization — reporting directly to leadership and coordinating closely with product and client teams.
        \item Designed and implemented the backend system from scratch using \textbf{Go}, \textbf{Kafka}, \textbf{MongoDB}, and \textbf{ClickHouse}.
        \item Built and tuned ClickHouse data models capable of handling 2,500+ events/sec to support real-time analytics and dashboards.
        \item Developed a high-throughput Kafka consumer to enrich 35,000+ events/sec before storage and further processing.
        \item Delivered a production-grade system with scalable architecture and low-latency performance under real traffic.
        \item \textbf{Tech stack:} Golang, PostgreSQL, Apache Kafka, Clickhouse, MongoDB
      \end{cvitems}
    }

    
  \cventry
    {Senior Software Engineer} % Job title
    {Vidoomy} % Organisation
    {Madrid, Spain} % Location
    {January 2024 - November 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed and maintained backend services for one of the most prominent ad networks in Spain
        \item Improved user synchronization pipeline, increasing identified users to 90\%.
        \item Led safe migration from `fasthttp` to `gin`, enhancing maintainability and readability.
        \item \textbf{Tech stack:} Golang, Redis, Apache Druid, Apache Kafka
      \end{cvitems}
    }

    
  \cventry
    {Software Engineer} % Job title
    {Ramzinex} % Organisation
    {Tehran, Iran} % Location
    {March 2023 - January 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Rewrote core trading services from legacy PHP to Golang with microservices approach, improving response time by 200ms.
        \item Mentored junior developers, performed code reviews, and supported their onboarding and growth.
        \item Established CI/CD pipelines and unit testing, reducing deployment errors to <5\%.
        \item \textbf{Tech stack:} Golang, PHP, Apache Kafka, Redis, MySQL
      \end{cvitems}
    }

    \cventry
    {Software Data Engineer} % Job title
    {Tapsell} % Organisation
    {Tehran, Iran} % Location
    {May 2021 - March 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed a large-scale data platform supporting 40M+ monthly active users with 10+ microservices.
        \item Designed stream processing applications handling 5,000+ events/sec using Kafka and Druid.
        \item Created gRPC and REST APIs for internal data services and model training pipelines.
        \item writing \textbf{Unit} and \textbf{Integration tests} and using \textbf{GitLab CI/CD} to ensure that code is deployed quickly and reliably
        \item \textbf{Tech stack:} Kotlin, Spring Boot, Apache Kafka, Apache Druid, Apache Kudu, Cassandra, MongoDB, Redis, Kubernetes
      \end{cvitems}
    }

    \cventry
    {Android Developer} % Job title
    {Oddrun | Mahsan} % Organisation
    {Tehran, Iran} % Location
    {November 2017 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Contributed to the development of multiple messaging and communication apps and SDKs.
        \item Implemented reactive features using Kotlin Coroutines and WebSocket.
        \item Built unit and integration tests alongside CI pipelines to ensure code quality.
        \item \textbf{Tech stack:} Kotlin, Java, JUnit, WebSocket, Reactive Programming
      \end{cvitems}
    }

\end{cventries}
